---
title: "Multiresidue analysis of pesticides in blood plasma using HF-LPME"
author: "Martha Zuluaga"
date: "2/26/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Environment
```{r}
library(tidyverse)
library(ggplot2)
library(ggfortify)
library(stats)
library(reshape2)
library(timeSeries)
library(purrr)
```

2. Call the data 
```{r}
raw.data <- read.csv("Data/rawData_Optim.csv") %>% 
  select(-1)
treatments <- read.csv("Data/HFtreatments.csv")
```

3. Data description and acquisition
This data comes from the GC/FID analysis performed to an extract of plasma samples based on the HF-LPME technique. 
The plasma was spiked with diferent pesticides (most of them organochlorines), then a HF-LPME technique was applied to extract the pesticides from the plasma samples. 
Other studies reported the variables that most influenced the extraction: Temperature, the velocity of stirring, time of extraction, and salt concentration (ref). Therefore, these variables were included in the experimental design.
According to the literature review, the range used in each variable were: 
Temperature: 20, 35, 50 ºC
The velocity of stirring: 500, 750, 100 rpm
Time of extraction: 5, 17.5, 30 min
Salt concentration: 5, 12.5, 20 %p/p
The variables were combined in a randomized block design.
Each treatment was repeated three times.
First we will make a descriptive analysis, and then we will find the best condition of extraction based on the variables measured. 

3.1. Descriptive analysis. Data distribution
```{r}

raw.1 <- raw.data %>% 
  select(-c(1:4))

treat <- as.data.frame(treatments[, 1])
colnames(treat) <- "treatment"
raw.1 <- cbind(treat, raw.1)

raw.melt <- melt(raw.1, id.vars= seq(1), measure.vars= seq(2, 12))
head(raw.melt)
```
```{r}
ggplot(raw.melt, aes(x = value, fill = variable)) + geom_density(alpha = 0.8) + xlim(-0.5, 2)
```

```{r}
ggplot(raw.melt, aes(x = value, fill = treatment)) + geom_density(alpha = 0.8) + xlim(-0.5, 2)
```
Figures exhibit a non normal distribution and variance heterogeneity. For this we will transform and normalize the data.

4. Data tidy and Normalization

First we will summarize the positives and zero values. To determine a strategy for data transformation. 
```{r}
raw.data %>% 
  summarize(pos = sum(.>0, na.rm = T),
            zero = sum(. == 0, na.rm = T),
            na = sum(is.na(.)))
```
As we have zeros into the data set we propose to transform the data based on the square root. Then, normalize and scale the data. For this we will use Pareto scale.

4.1. Square root transformation
```{r}
sqr_data <- raw.data %>% 
  select(-c(1:4)) %>% 
  map_df(sqrt)
```

4.2. Function for centering and scaling
```{r}
center_colmeans <- function(x) {
  xcenter = colMeans(x)
  x - rep(xcenter, rep.int(nrow(x), ncol(x)))
}
center_colpareto <- function(x) {
  xcenter = sqrt(colStdevs(x)) 
  x / rep(xcenter, rep.int(nrow(x), ncol(x)))
}

df.center <- center_colmeans(sqr_data)
Pareto.sqrt <- center_colpareto(df.center)
```

4.3. Data transformed visualization
```{r}
p_scale <- cbind(treat, Pareto.sqrt)

p_melt <- melt(p_scale, id.vars= seq(1), measure.vars= seq(2, 12))

ggplot(p_melt, aes(x = value, fill = variable)) + geom_density(alpha = 0.3, show.legend = TRUE) + xlim(-5, 5) 
```

5. Non-supervised analysis
5.1. Principal comoponent analysis with raw data 
```{r}
df.pca <- raw.data[, 5:15]
names(df.pca) <- c("Endosulfan", "Carbaryl", "Monocrotophos", "Carbofuran", "Lindane", "Aldrin", "Methyl.Parathion", "Dieldrin", "DDD", "DDT", "Endrin")

autoplot(prcomp(df.pca), loadings = TRUE, loadings.colour = 'black',
         loadings.label = TRUE, loadings.label.size = 5)

```

```{r}
pca <- princomp(df.pca, center= TRUE, scale= TRUE)
plot(pca, type="l")
```


```{r}
summary(pca)
```

5.2. Principal comoponent analysis with transformed data

```{r}
df.pca <- p_scale[, 2:12]
names(df.pca) <- c("Endosulfan", "Carbaryl", "Monocrotophos", "Carbofuran", "Lindane", "Aldrin", "Methyl.Parathion", "Dieldrin", "DDD", "DDT", "Endrin")

autoplot(prcomp(df.pca), loadings = TRUE, loadings.colour = 'black',
         loadings.label = TRUE, loadings.label.size = 5)
```

```{r}
pca <- princomp(df.pca, center= TRUE, scale= TRUE)
plot(pca, type="l")
```

```{r}
summary(pca)
```

In the descriptive analysis, whether we use the transformed data or the raw data, we find that carbaryl and lindane have a different and opposite extraction behavior, which also differs with the behavior of the rest of pesticides.










